manuscript_analysis_clean

### 2021-08-08 script/manuscript_clean_061021.Rmd
Update manuscript_clean_061021.Rmd
Changed variable names in the by-trial RT outlier removal function. This function is not necessary. Outliers were already removed in the data.

outlier_extract_trial_rt <-
  function(DF, task) {
    part_id <- DF[which(DF$task == task), "part_id"]

    if (length(part_id) != 0) {
    rt_trial <- rt_trial[-which(rt_trial$id %in% part_id & rt_trial$task == task), ]
    }
    return(rt_trial)
  }

>>>>

outlier_extract_trial_rt <-
  function(DF, taskName) {
    part_id <- DF[which(DF$task == taskName), "part_id"]

    if (length(which(rt_trial$id %in% part_id & rt_trial$task == taskName)) != 0) {
    rt_trial <- rt_trial[-which(rt_trial$id %in% part_id & rt_trial$task == taskName), ]
    }
    return(rt_trial)
  }
